Manuscript

### 2018-11-12 manuscript.Rmd
update pearson plotlys w/ abs and +/-

## Pearson correlation by lineage
```{r}
PearsonByLineage <- function(lin, dataset) {
  use_data <- filter(dataset, group_general_lineage_name == lin)
  use_data <- filter(use_data, !is.na(RPKM))
  use_data_summ <- use_data %>% count(Drug_Gene)
  use_data_summ <- filter(use_data_summ, n >= 3) # cor.test requires at least 3 non-NA data points
  use_data_filt <- filter(use_data, Drug_Gene %in% as.character(unique(use_data_summ$Drug_Gene)))
  if(nrow(use_data_filt) > 0) {
    pearson_res <- use_data_filt %>% group_by(Drug_Gene) %>% summarize(Pearson_Corr = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate, Pearson_Pval = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value)
    pearson_res <- merge(g2p_druggene_p_tally, pearson_res, all.y = TRUE)
    pearson_res$group_general_lineage_name <- lin
    return(pearson_res)
  }
}
```

@@

  plot_box <- ggplot(data = use_data) +
    facet_wrap(~ Dataset, drop = FALSE) +
    coord_cartesian(ylim = c(0, 1)) +
    scale_y_continuous(breaks = seq(0, 1, by = 0.1), labels = seq(0, 1, by = 0.1)) +
    geom_violin(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.5) +
    geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.75, width = 0.5) +
    coord_flip() +
    labs(x = "Level A G2P\nassociation") +
    theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))

@@

  use_data_ccle <- filter(use_data, Dataset == "CCLE")
  use_data_ccle_summ <- use_data_ccle %>% count(InG2P)
  if(nrow(use_data_ccle_summ) <= 1) {
    ccle_ttest_res <-  NA
    ticker <- ticker + 1
    }
  else if(use_data_ccle_summ[use_data_ccle_summ$InG2P == "Yes",]$nn < 2) { ccle_ttest_res <-  NA }
  else if(use_data_ccle_summ[use_data_ccle_summ$InG2P == "Yes",]$nn >= 2) {
    ccle_lin_ttest <- t.test(use_data_ccle$Pearson_Corr ~ use_data_ccle$InG2P)
    ccle_ttest_res <- paste0("t = ", round(ccle_lin_ttest$statistic, 3), ", df = ", round(ccle_lin_ttest$parameter, 3), ", p = ", round(ccle_lin_ttest$p.value, 3))
  }

  use_data_ctrp <- filter(use_data, Dataset == "CTRP")
  use_data_ctrp_summ <- use_data_ctrp %>% count(InG2P)
  if(nrow(use_data_ctrp_summ) <= 1) {
    ctrp_ttest_res <-  NA
    ticker <- ticker + 1
    }
  else if(use_data_ctrp_summ[use_data_ctrp_summ$InG2P == "Yes",]$nn < 2) { ctrp_ttest_res <-  NA }
  else if(use_data_ctrp_summ[use_data_ctrp_summ$InG2P == "Yes",]$nn >= 2) {
    ctrp_lin_ttest <- t.test(use_data_ctrp$Pearson_Corr ~ use_data_ctrp$InG2P)
    ctrp_ttest_res <- paste0("t = ", round(ctrp_lin_ttest$statistic, 3), ", df = ", round(ctrp_lin_ttest$parameter, 3), ", p = ", round(ctrp_lin_ttest$p.value, 3))
  }

  use_data_gdsc <- filter(use_data, Dataset == "GDSC")
  use_data_gdsc_summ <- use_data_gdsc %>% count(InG2P)
  if(nrow(use_data_gdsc_summ) <= 1) {
    gdsc_ttest_res <-  NA
    ticker <- ticker + 1
    }
  else if(use_data_gdsc_summ[use_data_gdsc_summ$InG2P == "Yes",]$nn < 2) { gdsc_ttest_res <-  NA }
  else if(use_data_gdsc_summ[use_data_gdsc_summ$InG2P == "Yes",]$nn >= 2) {
    gdsc_lin_ttest <- t.test(use_data_gdsc$Pearson_Corr ~ use_data_gdsc$InG2P)
    gdsc_ttest_res <- paste0("t = ", round(gdsc_lin_ttest$statistic, 3), ", df = ", round(gdsc_lin_ttest$parameter, 3), ", p = ", round(gdsc_lin_ttest$p.value, 3))
  }

  y_value <- ifelse(ticker == 3, 10, max(use_data$n) + 1)
  x_value <- (max(use_data$Pearson_Corr) + min(use_data$Pearson_Corr)) / 2

@@

  plot_point <- ggplot(data = use_data) +
    facet_wrap(~ Dataset, drop = FALSE) +
    scale_y_continuous(breaks = pretty_breaks()) +
    geom_point(mapping = aes(label = Pearson_Pvalue, color = InG2P, x = Pearson_Corr, y = n), alpha = 0.5, position = position_jitter(width = 0, height = 0.15)) +
    geom_text(data = summ_text, mapping = aes(x = x_value, y = y_value, label = Test_Results), nudge_y = 1) +
    labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations") +
    theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())

  plot_box <- ggplot(data = use_data) +
    facet_wrap(~ Dataset, drop = FALSE) +
    geom_violin(mapping = aes(color = InG2P, y = Pearson_Corr, x = InG2P), alpha = 0.5) +
    geom_boxplot(mapping = aes(color = InG2P, y = Pearson_Corr, x = InG2P), alpha = 0.5, width = 0.5) +
    coord_flip() +
    labs(x = "Level A G2P\nassociation") +
    theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))

@@

```{r}
ccle_druggene_mad_summ <- ccle_data_ptmuts %>% group_by(Drug_Gene, Mutation_Status_Nonsilent) %>% summarize(Mean_AUC = mean(AUC))
ccle_druggene_mad_summ <- dcast(ccle_druggene_mad_summ, Drug_Gene ~ Mutation_Status_Nonsilent)
ccle_druggene_mad_summ$MAD <- abs(ccle_druggene_mad_summ$Mutant - ccle_druggene_mad_summ$Other)
ccle_druggene_p_summ <- ccle_signif_g2p_ByDrug_all
ccle_druggene_p_summ$Drug_Gene <- paste0(ccle_druggene_p_summ$Drug, "_", ccle_druggene_p_summ$Hugo_Symbol)
ccle_druggene_summ <- merge(merge(g2p_druggene_p_tally, ccle_druggene_p_summ[, c("Drug_Gene", "p")], by = "Drug_Gene", all.y = TRUE), ccle_druggene_mad_summ, by = "Drug_Gene", all = TRUE)
ccle_druggene_summ$n <- ifelse(is.na(ccle_druggene_summ$n), 0, ccle_druggene_summ$n)
ccle_druggene_summ$InG2P <- ifelse(ccle_druggene_summ$n != 0, "Yes", "No")
ccle_druggene_summ$Dataset <- "CCLE"
ccle_p_ttest <- t.test(ccle_druggene_summ$p ~ ccle_druggene_summ$InG2P)
ccle_p_ttest_res <- paste0("t = ", round(ccle_p_ttest$statistic, 3), ", df = ", round(ccle_p_ttest$parameter, 3), ", p = ", round(ccle_p_ttest$p.value, 3))
ccle_mad_ttest <- t.test(ccle_druggene_summ$MAD ~ ccle_druggene_summ$InG2P)
ccle_mad_ttest_res <- paste0("t = ", round(ccle_mad_ttest$statistic, 3), ", df = ", round(ccle_mad_ttest$parameter, 3), ", p = ", round(ccle_mad_ttest$p.value, 3))

ctrp_druggene_mad_summ <- ctrp_data_ptmuts %>% group_by(Drug_Gene, Mutation_Status_Nonsilent) %>% summarize(Mean_AUC = mean(AUC))
ctrp_druggene_mad_summ <- dcast(ctrp_druggene_mad_summ, Drug_Gene ~ Mutation_Status_Nonsilent)
ctrp_druggene_mad_summ$MAD <- abs(ctrp_druggene_mad_summ$Mutant - ctrp_druggene_mad_summ$Other)
ctrp_druggene_p_summ <- ctrp_signif_g2p_ByDrug_all
ctrp_druggene_p_summ$Drug_Gene <- paste0(ctrp_druggene_p_summ$Drug, "_", ctrp_druggene_p_summ$Hugo_Symbol)
ctrp_druggene_summ <- merge(merge(g2p_druggene_p_tally, ctrp_druggene_p_summ[, c("Drug_Gene", "p")], by = "Drug_Gene", all.y = TRUE), ctrp_druggene_mad_summ, by = "Drug_Gene", all = TRUE)
ctrp_druggene_summ$n <- ifelse(is.na(ctrp_druggene_summ$n), 0, ctrp_druggene_summ$n)
ctrp_druggene_summ$InG2P <- ifelse(ctrp_druggene_summ$n != 0, "Yes", "No")
ctrp_druggene_summ$Dataset <- "CTRP"
ctrp_p_ttest <- t.test(ctrp_druggene_summ$p ~ ctrp_druggene_summ$InG2P)
ctrp_p_ttest_res <- paste0("t = ", round(ctrp_p_ttest$statistic, 3), ", df = ", round(ctrp_p_ttest$parameter, 3), ", p = ", round(ctrp_p_ttest$p.value, 3))
ctrp_mad_ttest <- t.test(ctrp_druggene_summ$MAD ~ ctrp_druggene_summ$InG2P)
ctrp_mad_ttest_res <- paste0("t = ", round(ctrp_mad_ttest$statistic, 3), ", df = ", round(ctrp_mad_ttest$parameter, 3), ", p = ", round(ctrp_mad_ttest$p.value, 3))

gdsc_druggene_mad_summ <- gdsc_data_ptmuts %>% group_by(Drug_Gene, Mutation_Status_Nonsilent) %>% summarize(Mean_AUC = mean(AUC))
gdsc_druggene_mad_summ <- dcast(gdsc_druggene_mad_summ, Drug_Gene ~ Mutation_Status_Nonsilent)
gdsc_druggene_mad_summ$MAD <- abs(gdsc_druggene_mad_summ$Mutant - gdsc_druggene_mad_summ$Other)
gdsc_druggene_p_summ <- gdsc_signif_g2p_ByDrug_all
gdsc_druggene_p_summ$Drug_Gene <- paste0(gdsc_druggene_p_summ$Drug, "_", gdsc_druggene_p_summ$Hugo_Symbol)
gdsc_druggene_summ <- merge(merge(g2p_druggene_p_tally, gdsc_druggene_p_summ[, c("Drug_Gene", "p")], by = "Drug_Gene", all.y = TRUE), gdsc_druggene_mad_summ, by = "Drug_Gene", all = TRUE)
gdsc_druggene_summ$n <- ifelse(is.na(gdsc_druggene_summ$n), 0, gdsc_druggene_summ$n)
gdsc_druggene_summ$InG2P <- ifelse(gdsc_druggene_summ$n != 0, "Yes", "No")
gdsc_druggene_summ$Dataset <- "GDSC"
gdsc_p_ttest <- t.test(gdsc_druggene_summ$p ~ gdsc_druggene_summ$InG2P)
gdsc_p_ttest_res <- paste0("t = ", round(gdsc_p_ttest$statistic, 3), ", df = ", round(gdsc_p_ttest$parameter, 3), ", p = ", round(gdsc_p_ttest$p.value, 3))
gdsc_mad_ttest <- t.test(gdsc_druggene_summ$MAD ~ gdsc_druggene_summ$InG2P)
gdsc_mad_ttest_res <- paste0("t = ", round(gdsc_mad_ttest$statistic, 3), ", df = ", round(gdsc_mad_ttest$parameter, 3), ", p = ", round(gdsc_mad_ttest$p.value, 3))

@@

g2p_druggene_pearson <- rbind(ccle_pearson_res, ctrp_pearson_res, gdsc_pearson_res)
g2p_druggene_pearson_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"), Test_Results_PearCorr = c(ccle_pearson_ttest_res, ctrp_pearson_ttest_res, gdsc_pearson_ttest_res))
```

```{r fig.height=5, fig.width=12}
plot_pearson_point <- ggplot(data = g2p_druggene_pearson) +
  facet_wrap(~ Dataset) +
  geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = Pearson_Corr, y = n), alpha = 0.5) +
  scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
  scale_x_continuous(breaks = pretty_breaks()) +
  geom_text(data = g2p_druggene_pearson_text, mapping = aes(x = -0.05, y = 110, label = Test_Results_PearCorr)) +
  labs(x = "Pearson correlation coefficient between drug-gene AUC and gene expression", y = "Number of level A G2P associations") +
  theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())

plot_pearson_box <- ggplot(data = g2p_druggene_pearson) +
  facet_wrap(~ Dataset) +
  geom_violin(mapping = aes(color = InG2P, y = Pearson_Corr, x = InG2P), alpha = 0.5) +
  geom_boxplot(mapping = aes(color = InG2P, y = Pearson_Corr, x = InG2P), alpha = 0.5, width = 0.25) +
  coord_flip() +
  labs(x = "Level A G2P\nassociation") +
  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))

@@

```{r, eval=FALSE}
plot_pearson_point <- ggplot(data = g2p_druggene_pearson) +
  facet_wrap(~ Dataset) +
  geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = Pearson_Corr, y = n), alpha = 0.5) +
  scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
  scale_x_continuous(breaks = pretty_breaks()) +
  geom_text(data = g2p_druggene_pearson_text, mapping = aes(x = -0.05, y = 110, label = Test_Results_PearCorr)) +
  labs(x = "Pearson correlation coefficient between drug-gene AUC and gene expression", y = "Number of level A G2P associations") +
  theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())

plot_pearson_box <- ggplot(data = g2p_druggene_pearson) +
  facet_wrap(~ Dataset) +
  geom_violin(mapping = aes(color = InG2P, y = Pearson_Corr, x = InG2P), alpha = 0.5) +
  geom_boxplot(mapping = aes(color = InG2P, y = Pearson_Corr, x = InG2P), alpha = 0.5, width = 0.25) +
  coord_flip() +
  labs(x = "Level A G2P\nassociation") +
  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))

>>>>

## Pearson correlation by lineage
```{r}
PearsonByLineage <- function(lin, dataset) {
  use_data <- filter(dataset, group_general_lineage_name == lin)
  use_data <- filter(use_data, !is.na(RPKM))
  use_data_summ <- use_data %>% count(Drug_Gene)
  use_data_summ <- filter(use_data_summ, n >= 3) # cor.test requires at least 3 non-NA data points
  use_data_filt <- filter(use_data, Drug_Gene %in% as.character(unique(use_data_summ$Drug_Gene)))
  if(nrow(use_data_filt) > 0) {
    pearson_res <- use_data_filt %>% group_by(Drug_Gene) %>% summarize(Pearson_Corr = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate, Pearson_Pval = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value)
    pearson_res <- merge(g2p_druggene_p_tally, pearson_res, all.y = TRUE)
    pearson_res$group_general_lineage_name <- lin
    pearson_res$Pearson_Corr_Abs <- abs(pearson_res$Pearson_Corr)
    pearson_res$Pearson_Corr_Sign <- ifelse(sign(pearson_res$Pearson_Corr) == 1, "+",
                                            ifelse(sign(pearson_res$Pearson_Corr) == -1, "-", "0"))
    return(pearson_res)
  }
}
```

@@

  plot_box <- ggplot(data = use_data) +
    facet_wrap(~ Dataset, drop = FALSE) +
    coord_cartesian(ylim = c(0, 1)) +
    scale_y_continuous(breaks = seq(0, 1, by = 0.1), labels = seq(0, 1, by = 0.1)) +
    geom_violin(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.5) +
    geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.75, width = 0.25) +
    coord_flip() +
    labs(x = "Level A G2P\nassociation") +
    theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))

@@

  use_data_ccle <- filter(use_data, Dataset == "CCLE")
  use_data_ccle_summ <- use_data_ccle %>% count(InG2P)
  if(nrow(use_data_ccle_summ) <= 1) {
    ccle_ttest_res <-  NA
    ticker <- ticker + 1
    }
  else if(use_data_ccle_summ[use_data_ccle_summ$InG2P == "Yes",]$nn < 2) { ccle_ttest_res <-  NA }
  else if(use_data_ccle_summ[use_data_ccle_summ$InG2P == "Yes",]$nn >= 2) {
    ccle_lin_ttest <- t.test(use_data_ccle$Pearson_Corr_Abs ~ use_data_ccle$InG2P)
    ccle_ttest_res <- paste0("t = ", round(ccle_lin_ttest$statistic, 3), ", df = ", round(ccle_lin_ttest$parameter, 3), ", p = ", round(ccle_lin_ttest$p.value, 3))
  }

  use_data_ctrp <- filter(use_data, Dataset == "CTRP")
  use_data_ctrp_summ <- use_data_ctrp %>% count(InG2P)
  if(nrow(use_data_ctrp_summ) <= 1) {
    ctrp_ttest_res <-  NA
    ticker <- ticker + 1
    }
  else if(use_data_ctrp_summ[use_data_ctrp_summ$InG2P == "Yes",]$nn < 2) { ctrp_ttest_res <-  NA }
  else if(use_data_ctrp_summ[use_data_ctrp_summ$InG2P == "Yes",]$nn >= 2) {
    ctrp_lin_ttest <- t.test(use_data_ctrp$Pearson_Corr_Abs ~ use_data_ctrp$InG2P)
    ctrp_ttest_res <- paste0("t = ", round(ctrp_lin_ttest$statistic, 3), ", df = ", round(ctrp_lin_ttest$parameter, 3), ", p = ", round(ctrp_lin_ttest$p.value, 3))
  }

  use_data_gdsc <- filter(use_data, Dataset == "GDSC")
  use_data_gdsc_summ <- use_data_gdsc %>% count(InG2P)
  if(nrow(use_data_gdsc_summ) <= 1) {
    gdsc_ttest_res <-  NA
    ticker <- ticker + 1
    }
  else if(use_data_gdsc_summ[use_data_gdsc_summ$InG2P == "Yes",]$nn < 2) { gdsc_ttest_res <-  NA }
  else if(use_data_gdsc_summ[use_data_gdsc_summ$InG2P == "Yes",]$nn >= 2) {
    gdsc_lin_ttest <- t.test(use_data_gdsc$Pearson_Corr_Abs ~ use_data_gdsc$InG2P)
    gdsc_ttest_res <- paste0("t = ", round(gdsc_lin_ttest$statistic, 3), ", df = ", round(gdsc_lin_ttest$parameter, 3), ", p = ", round(gdsc_lin_ttest$p.value, 3))
  }

@@

  plot_point <- ggplot(data = use_data) +
    facet_wrap(~ Dataset, drop = FALSE) +
    scale_y_continuous(breaks = pretty_breaks()) +
    geom_point(mapping = aes(label = Pearson_Pvalue, color = InG2P, shape = Pearson_Corr_Sign, x = Pearson_Corr_Abs, y = n), alpha = 0.5, position = position_jitter(width = 0, height = 0.15)) +
    scale_shape_manual(values = c(45, 43, 42)) +
    geom_text(data = summ_text, mapping = aes(x = 0.5, y = y_value, label = Test_Results), nudge_y = 1) +
    labs(y = "Number of level A G2P associations") +
    theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())

  plot_box <- ggplot(data = use_data) +
    facet_wrap(~ Dataset, drop = FALSE) +
    geom_violin(mapping = aes(color = InG2P, y = Pearson_Corr_Abs, x = InG2P), alpha = 0.5) +
    geom_boxplot(mapping = aes(color = InG2P, y = Pearson_Corr_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
    coord_flip() +
    labs(x = "Level A G2P\nassociation") +
    theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))

@@

```{r}
ccle_druggene_mad_summ <- ccle_data_ptmuts %>% group_by(Drug_Gene, Mutation_Status_Nonsilent) %>% summarize(Mean_AUC = mean(AUC))
ccle_druggene_mad_summ <- dcast(ccle_druggene_mad_summ, Drug_Gene ~ Mutation_Status_Nonsilent)
ccle_druggene_mad_summ$MAD <- abs(ccle_druggene_mad_summ$Mutant - ccle_druggene_mad_summ$Other)
ccle_druggene_p_summ <- ccle_signif_g2p_lineage
ccle_druggene_p_summ$Drug_Gene <- paste0(ccle_druggene_p_summ$Drug, "_", ccle_druggene_p_summ$Hugo_Symbol)
ccle_druggene_summ <- merge(merge(g2p_druggene_p_tally, ccle_druggene_p_summ[, c("Drug_Gene", "p")], by = "Drug_Gene", all.y = TRUE), ccle_druggene_mad_summ, by = "Drug_Gene", all = TRUE)
ccle_druggene_summ$n <- ifelse(is.na(ccle_druggene_summ$n), 0, ccle_druggene_summ$n)
ccle_druggene_summ$InG2P <- ifelse(ccle_druggene_summ$n != 0, "Yes", "No")
ccle_druggene_summ$Dataset <- "CCLE"
ccle_p_ttest <- t.test(ccle_druggene_summ$p ~ ccle_druggene_summ$InG2P)
ccle_p_ttest_res <- paste0("t = ", round(ccle_p_ttest$statistic, 3), ", df = ", round(ccle_p_ttest$parameter, 3), ", p = ", round(ccle_p_ttest$p.value, 3))
ccle_mad_ttest <- t.test(ccle_druggene_summ$MAD ~ ccle_druggene_summ$InG2P)
ccle_mad_ttest_res <- paste0("t = ", round(ccle_mad_ttest$statistic, 3), ", df = ", round(ccle_mad_ttest$parameter, 3), ", p = ", round(ccle_mad_ttest$p.value, 3))

ctrp_druggene_mad_summ <- ctrp_data_ptmuts %>% group_by(Drug_Gene, Mutation_Status_Nonsilent) %>% summarize(Mean_AUC = mean(AUC))
ctrp_druggene_mad_summ <- dcast(ctrp_druggene_mad_summ, Drug_Gene ~ Mutation_Status_Nonsilent)
ctrp_druggene_mad_summ$MAD <- abs(ctrp_druggene_mad_summ$Mutant - ctrp_druggene_mad_summ$Other)
ctrp_druggene_p_summ <- ctrp_signif_g2p_lineage
ctrp_druggene_p_summ$Drug_Gene <- paste0(ctrp_druggene_p_summ$Drug, "_", ctrp_druggene_p_summ$Hugo_Symbol)
ctrp_druggene_summ <- merge(merge(g2p_druggene_p_tally, ctrp_druggene_p_summ[, c("Drug_Gene", "p")], by = "Drug_Gene", all.y = TRUE), ctrp_druggene_mad_summ, by = "Drug_Gene", all = TRUE)
ctrp_druggene_summ$n <- ifelse(is.na(ctrp_druggene_summ$n), 0, ctrp_druggene_summ$n)
ctrp_druggene_summ$InG2P <- ifelse(ctrp_druggene_summ$n != 0, "Yes", "No")
ctrp_druggene_summ$Dataset <- "CTRP"
ctrp_p_ttest <- t.test(ctrp_druggene_summ$p ~ ctrp_druggene_summ$InG2P)
ctrp_p_ttest_res <- paste0("t = ", round(ctrp_p_ttest$statistic, 3), ", df = ", round(ctrp_p_ttest$parameter, 3), ", p = ", round(ctrp_p_ttest$p.value, 3))
ctrp_mad_ttest <- t.test(ctrp_druggene_summ$MAD ~ ctrp_druggene_summ$InG2P)
ctrp_mad_ttest_res <- paste0("t = ", round(ctrp_mad_ttest$statistic, 3), ", df = ", round(ctrp_mad_ttest$parameter, 3), ", p = ", round(ctrp_mad_ttest$p.value, 3))

gdsc_druggene_mad_summ <- gdsc_data_ptmuts %>% group_by(Drug_Gene, Mutation_Status_Nonsilent) %>% summarize(Mean_AUC = mean(AUC))
gdsc_druggene_mad_summ <- dcast(gdsc_druggene_mad_summ, Drug_Gene ~ Mutation_Status_Nonsilent)
gdsc_druggene_mad_summ$MAD <- abs(gdsc_druggene_mad_summ$Mutant - gdsc_druggene_mad_summ$Other)
gdsc_druggene_p_summ <- gdsc_signif_g2p_lineage
gdsc_druggene_p_summ$Drug_Gene <- paste0(gdsc_druggene_p_summ$Drug, "_", gdsc_druggene_p_summ$Hugo_Symbol)
gdsc_druggene_summ <- merge(merge(g2p_druggene_p_tally, gdsc_druggene_p_summ[, c("Drug_Gene", "p")], by = "Drug_Gene", all.y = TRUE), gdsc_druggene_mad_summ, by = "Drug_Gene", all = TRUE)
gdsc_druggene_summ$n <- ifelse(is.na(gdsc_druggene_summ$n), 0, gdsc_druggene_summ$n)
gdsc_druggene_summ$InG2P <- ifelse(gdsc_druggene_summ$n != 0, "Yes", "No")
gdsc_druggene_summ$Dataset <- "GDSC"
gdsc_p_ttest <- t.test(gdsc_druggene_summ$p ~ gdsc_druggene_summ$InG2P)
gdsc_p_ttest_res <- paste0("t = ", round(gdsc_p_ttest$statistic, 3), ", df = ", round(gdsc_p_ttest$parameter, 3), ", p = ", round(gdsc_p_ttest$p.value, 3))
gdsc_mad_ttest <- t.test(gdsc_druggene_summ$MAD ~ gdsc_druggene_summ$InG2P)
gdsc_mad_ttest_res <- paste0("t = ", round(gdsc_mad_ttest$statistic, 3), ", df = ", round(gdsc_mad_ttest$parameter, 3), ", p = ", round(gdsc_mad_ttest$p.value, 3))

@@

g2p_druggene_pearson <- rbind(ccle_pearson_res, ctrp_pearson_res, gdsc_pearson_res)
g2p_druggene_pearson$Pearson_Corr_Abs <- abs(g2p_druggene_pearson$Pearson_Corr)
g2p_druggene_pearson$Pearson_Corr_Sign <- ifelse(sign(g2p_druggene_pearson$Pearson_Corr) == 1, "+",
                                           ifelse(sign(g2p_druggene_pearson$Pearson_Corr) == -1, "-", "0"))
g2p_druggene_pearson_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"), Test_Results_PearCorr = c(ccle_pearson_ttest_res, ctrp_pearson_ttest_res, gdsc_pearson_ttest_res))
```

```{r fig.height=5, fig.width=12}
plot_pearson_point <- ggplot(data = g2p_druggene_pearson) +
  facet_wrap(~ Dataset) +
  geom_point(mapping = aes(label = Drug_Gene, color = InG2P, shape = Pearson_Corr_Sign, x = Pearson_Corr_Abs, y = n)) +
  scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
  scale_x_continuous(breaks = pretty_breaks()) +
  scale_shape_manual(values = c(45, 43, 42)) +
  geom_text(data = g2p_druggene_pearson_text, mapping = aes(x = 0.3, y = 110, label = Test_Results_PearCorr)) +
  labs(x = "Pearson correlation coefficient between drug-gene AUC and gene expression", y = "Number of level A G2P associations") +
  theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())

plot_pearson_box <- ggplot(data = g2p_druggene_pearson) +
  facet_wrap(~ Dataset) +
  geom_violin(mapping = aes(color = InG2P, y = Pearson_Corr_Abs, x = InG2P), alpha = 0.5) +
  geom_boxplot(mapping = aes(color = InG2P, y = Pearson_Corr_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
  coord_flip() +
  labs(x = "Level A G2P\nassociation") +
  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))

@@

```{r, eval=FALSE}
plot_pearson_point <- ggplot(data = g2p_druggene_pearson) +
  facet_wrap(~ Dataset) +
  geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = Pearson_Corr_Abs, shape = Pearson_Corr_Sign, y = n), alpha = 0.5) +
  scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
  scale_x_continuous(breaks = pretty_breaks()) +
  scale_shape_manual(values = c(45, 43, 42)) +
  geom_text(data = g2p_druggene_pearson_text, mapping = aes(x = 0.3, y = 110, label = Test_Results_PearCorr)) +
  labs(x = "Pearson correlation coefficient between drug-gene AUC and gene expression", y = "Number of level A G2P associations") +
  theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())

plot_pearson_box <- ggplot(data = g2p_druggene_pearson) +
  facet_wrap(~ Dataset) +
  geom_violin(mapping = aes(color = InG2P, y = Pearson_Corr_Abs, x = InG2P), alpha = 0.5) +
  geom_boxplot(mapping = aes(color = InG2P, y = Pearson_Corr_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
  coord_flip() +
  labs(x = "Level A G2P\nassociation") +
  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
